\myTitle

### 2014-08-08 tex/author-title-etc.tex
Substantial edits to shorten introduction, etc.
Minor edits
Wrangled everything to get a single-column submission version, too.

%%%%% THIS IS THE SECTION WHERE THE AUTHOR PUTS IN ALL OF THEIR TITLE AND AFFILIATION
%%%%% INFORMATION AND  A FEW OTHER THINGS
\newcommand{\myTitle}{A statistically-grounded interpretation of {\sc flock}}

% redefine this to make author list. Note affiliation symbols are done manually.
% All caps tends to look better
\newcommand{\myAuthors}{ ERIC C.~ANDERSON$^{*,\dagger,\S}$ and PATRICK D. BARRY$^\ddag$}

% redefine to make the affiliation list.  Note symbols are done manually
\newcommand{\myAffiliations}{$^*$Fisheries Ecology Division, 
    Southwest Fisheries Science Center, National Marine Fisheries Service, NOAA,
    110 Shaffer Road,
    Santa Cruz, CA 95060, USA, $^\dagger$Department of Applied Math and Statistics, University of
California, Santa Cruz, CA, $^\ddag$University of Alaska, Fairbanks, School of Fisheries and Ocean Science,
17101 Point Lena Loop Rd.,
Juneau, AK 99801, USA }

@@

% here you can put a running title (a short title that goes on the left of the 
% even pages)
\newcommand{\myRunningTitle}{{\sc flock} as a special case of {\sc structure}}

>>>>

%%%%% THIS IS THE SECTION WHERE THE AUTHOR PUTS IN ALL OF THEIR TITLE AND AFFILIATION
%%%%% INFORMATION AND  A FEW OTHER THINGS
\newcommand{\myTitle}{Interpreting the {\sc flock} algorithm from a statistical \\ perspective}
\title{\myTitle}

% redefine this to make author list. Note affiliation symbols are done manually.
% All caps tends to look better
\newcommand{\myAuthors}{ ERIC C.~ANDERSON$^{*,\S}$ and PATRICK D. BARRY$^\dagger$}
\author{ERIC C.~ANDERSON$^{*}$ and PATRICK D. BARRY$^\dagger$}

% redefine to make the affiliation list.  Note symbols are done manually
\newcommand{\myAffiliations}{$^*$Fisheries Ecology Division, 
    Southwest Fisheries Science Center, National Marine Fisheries Service, NOAA,
    110 Shaffer Road,
    Santa Cruz, CA 95060, USA, $^\dagger$University of Alaska, Fairbanks, School of Fisheries and Ocean Science,
17101 Point Lena Loop Rd.,
Juneau, AK 99801, USA }
\renewcommand{\AuthorAddresses}{\myAffiliations}

\renewcommand{\KeyWords}{Unsupervised clustering, simulated annealing, software}

\renewcommand{\CorrespondingAuthor}{Eric C. Anderson, Fisheries Ecology Division, Southwest Fisheries Science
Center, 110 Shaffer Road, Santa Cruz, CA 95060. eric.anderson@noaa.gov}

@@

% here you can put a running title (a short title that goes on the left of the 
% even pages)
\newcommand{\myRunningTitle}{A statistical perspective on {\sc flock}}
\renewcommand{\RunningTitle}{\myRunningTitle}
